\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation

### 2018-07-29 ndss/eval.tex
ccs comments.

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM. When we compare our execution times with prior protocols, we match our system and network parameters with those of the prior work (as the code for works such as Bost et al. \cite{shafindss} and \minion~\cite{minionn} are not publicly available).
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Most of our benchmarks
are related to machine learning and we set up (largely standard) notation and describe our benchmarks in \appendixref{benchmarks}.

>>>>

We present the numbers for two network settings, a LAN setting and
a cross-continent WAN setting. The round trip time between the server
and the client machines in the two settings is 1ms and 40ms respectively. Each
machine has an Intel(R) Xeon(R) CPU E5-2673 v3 processor running at
2.40GHz with 28 GBs of RAM. When we compare our execution times with prior protocols, we match our system and network parameters with those of the prior work (as the code for works such as Bost et al. \cite{shafindss} and \minion~\cite{minionn} are not publicly available).
%
%% The  \tool compiler is written in Python and
%% compiles each of our benchmarks in under a second to C++ code that makes calls to the ABY
%% library~\cite{aby}. We use an off-the-shelf solver
%% (SeaHorn~\cite{seahorn}) to check the verification conditions required
%% to prove that the array indices remain in bound. The solver takes less
%% than a minute on our largest benchmark.
Most of our benchmarks
are related to machine learning. We set up (largely standard) notation and describe our benchmarks in \appendixref{benchmarks}.

### 2018-07-29 ndss/ex.tex
added ndss version.
ccs comments.

The compiler splits the input
program into \emph{public} and \emph{secret} components. The public
components translate into regular C++ code, while the secret
components translate into API calls into our \mpc back-end
(ABY). For example, in \figureref{ex-sml}, the \tool
compiler realizes that the array index \ls{i} in the inner product loop
is public, and hence the access locations need not be hidden.
Therefore, it compiles the \ls{for}~loop into a C++
\ls{for}~loop that will be executed in-clear
(line~\ref{line:dotproductloop}).

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao, we elaborate in
\sectionref{impl}). We elaborate on cryptographic cost awareness in
\sectionref{ccc}.

@@

\noindent\textbf{Advantages of \tool} We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program and get the code right in
\figureref{ex-sml}, rather than the code in
\figureref{ex-aby}.
% (as we mentioned in Section~\ref{sec:intro},
%other high-level languages are limited in their use of a single,
%arithmetic or boolean, crypto back-end). 
\tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in \figureref{ex-sml} a
change from multiplication to bitwise-or in the \ls{for} loop. It
turns out that in this case, it is more efficient to do both
the addition and bitwise-or using boolean circuits (if the addition is
done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or would have to
revisit many parts of the circuit and change them. In summary, \tool raises the level of abstraction for the
programmer, and generates efficient \mpc protocols automatically,
while its metatheory provides strong correctness and security
guarantees.

@@

The largest benchmark in CBMC-GC is a multiplication of two $8\times 8$ matrices for which it generates about a million gates and takes about ten seconds to run. In contrast, \tool uses arithmetic sharing, generates 1218 gates, and runs in less than 0.1 seconds. When we tried multiplying two $20\times 20$ matrices with CBMC-GC, it timed out after 5 hours. Our benchmarks require much bigger computations (e.g., multiplying a $64\times576$ matrix with a $576\times1024$ matrix). Unlike CBMC-GC, ObliVM can scale to larger benchmarks (because it uses Yao-pipelining \cite{yao-pipe}). We evaluated the program in \figureref{ex-sml} with vectors of lengths varying between $10^3$ and $10^6$ using both \tool and ObliVM. 
\tool evaluates the inner-product in arithmetic and, empirically, is at least 25x faster than ObliVM.

>>>>

The compiler splits the input
program into \emph{public} and \emph{secret} components. The public
components translate into regular C++ code, while the secret
components translate into API calls into our \mpc back-end
(ABY). For example, in \figureref{ex-sml}, the \tool
compiler realizes that the array index \ls{i} in the inner product loop
is public, and hence the access locations need not be hidden.
Therefore, it compiles the \ls{for}~loop into a C++
\ls{for}~loop that will be executed in-clear
(line~\ref{line:dotproductloop}). We remark that, in our experiments, assigning public labels to control flow variables is critical for performance and/or security. However, we have observed that conservatively creating circuits for other public variables incurs minimal cost in practice.

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-components. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao, we elaborate in
\sectionref{impl}). At the expression level, \tool provides secret conditionals (using the '? :' operator) which are implemented using multiplexers, while secret dependent array accesses can also be implemented using the '? :' operator. We elaborate on cryptographic cost awareness in
\sectionref{ccc}.

@@

\noindent\textbf{Advantages of \tool.} We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program and get the code right in
\figureref{ex-sml}, rather than the code in
\figureref{ex-aby}.
% (as we mentioned in Section~\ref{sec:intro},
%other high-level languages are limited in their use of a single,
%arithmetic or boolean, crypto back-end). 
\tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in \figureref{ex-sml} a
change from multiplication to bitwise-or in the \ls{for} loop. It
turns out that in this case, it is more efficient to do both
the addition and bitwise-or using boolean circuits (if the addition is
done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or would have to
revisit many parts of the circuit and change them. In summary, \tool raises the level of abstraction for the
programmer, and generates efficient \mpc protocols automatically,
while its metatheory provides strong correctness and security
guarantees.

@@

The largest benchmark in CBMC-GC is a multiplication of two $8\times 8$ matrices for which it generates about a million gates and takes about ten seconds to run. In contrast, \tool uses arithmetic sharing, generates 1218 gates, and runs in less than 0.1 seconds. When we tried multiplying two $20\times 20$ matrices with CBMC-GC, it timed out after 5 hours. Our benchmarks require much bigger computations (e.g., multiplying a $64\times576$ matrix with a $576\times1024$ matrix). Unlike CBMC-GC, ObliVM can scale to larger benchmarks (because it uses Yao-pipelining \cite{yao-pipe}). We evaluated the program in \figureref{ex-sml} with vectors of lengths varying between $10^3$ and $10^6$ using both \tool and ObliVM. 
\tool evaluates the inner-product in arithmetic and, empirically, is at least 25x faster than ObliVM on the same hardware.

\subsection{Comparison with handwritten ABY code}

We have evaluated against handwritten ABY code for the examples in the ABY repository and \tool has comparable performance. However, these examples are not representative of practical ML tasks. Writing sophisticated ML applications such as neural networks in ABY is a very tedious and nearly impossible engineering task even for crypto experts -- automating the same is our main contribution.

### 2018-07-29 ndss/intro.tex
added ndss version.
ccs comments.

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' compiler that generates efficient and
scalable \mpc protocols using combinations of
arithmetic and boolean circuits. \tool is backed by a formal model
that enables it to choose arithmetic or boolean representations for
different parts of
the program, while automatically inserting inter-conversion gates as
necessary. In addition to guiding the compiler, the formal model also
provides strong correctness and
security theorems. Our comprehensive evaluation shows that the
automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
Below we describe
the salient features of \tool.

@@

\noindent\textbf{Ease of programming.} \tool source programs are ideal
functionalities that describe ``what'' computation needs to be done,
rather than ``how'' to do it. In particular, the programmer writes the
high-level computation without thinking about the underlying
cryptographic details. For example, \figureref{ex-sml}
shows an \tool source
program for $w^Tx >b$. The program is quite similar to what a programmer might
write in C++ or Java. The simplicity of the
language comes with the usual benefits: it is easily accessible to the
developers, there are fewer avenues for making mistakes, developers
don't bear the burden of getting cryptographic details right, 
code optimizations can be left to the compiler,
and it
is easy to maintain and modify the programs. Needless to say,
frameworks that expose low-level circuit APIs to the programmer do not
enjoy these benefits.

\noindent\textbf{Cryptographic-cost aware compiler.} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and generates non-cryptographic code for the array accesses.
Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an efficient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic-cost aware compiler.

\noindent\textbf{Scalability (secure code partitioning).} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool. 
%\aseem{What about the differences from Yao pipelining? Worth
%adding here that it is a backend-agnostic technique?}

@@

\noindent\textbf{Formal guarantees.} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for all well-typed source programs, the two semantics
successfully terminate
(e.g., there are no array index out-of-bounds errors) with identical
observable outputs. For
the security theorem, we formally reduce the security
of our scheme against semi-honest (or ``honest but curious")
adversaries to the semi honest security of the  \mpc back-end. The
theorem provides protection against side-channels arising from
conditionals and memory access patterns.
 We also prove a formal security theorem against semi-honest
 adversaries for our partitioning
scheme (\sectionref{ld} and~\sectionref{pipe}).

\noindent\textbf{Evaluation.} We have implemented \tool
using ABY~\cite{aby} as the
cryptographic back-end.
We compare \tool with Yao-based compilers in~\sectionref{oblivm}
and with specialized protocols in~\sectionref{eval}. 
 We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers from Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also the matrix factorization example
from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of \bonsai~\cite{bonsai}, and it was programmed in the
high-level \tool source language by a non-cryptographer. Second, the
performance
of the protocols
generated by \tool are comparable to or better than (up to 19x) their state-of-the-art, hand-crafted implementations. Finally, we
demonstrate the usefulness of partitioning by implementing an application
that requires more than 300 million gates (\sectionref{impl} and~\sectionref{eval}).

\noindent\textbf{Related Work.}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} observe, due
 to the high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries that lack formal semantics and static guarantees.
Finally, we focus on the language
features necessary to implement machine learning applications.
In particular, we do not discuss declassification of
intermediate values or indexing into arrays at secret indices.
 Handling them requires additional complexity. For example,
Wysteria~\cite{wysteria} handles the former using dependent types
and ObliVM~\cite{oblivm} uses Oblivious RAM for the latter.
These situations seldomly arise in the machine learning applications that we consider:
intermediate values don't need to be declassified and arrays are traversed in an oblivious manner. We provide a detailed survey of related
work in \sectionref{related}.

>>>>

\subsection{Our Contributions}
This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' compiler that generates efficient and
scalable \mpc protocols using combinations of
arithmetic and boolean circuits. \tool is backed by a formal model
that enables it to choose arithmetic or boolean representations for
different parts of
the program, while automatically inserting inter-conversion gates as
necessary. In addition to guiding the compiler, the formal model also
provides strong correctness and
security theorems. Our comprehensive evaluation shows that the
automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
Below we describe
the salient features of \tool.

@@

\subsubsection{Ease of programming} \tool source programs are ideal
functionalities that describe ``what'' computation needs to be done,
rather than ``how'' to do it. In particular, the programmer writes the
high-level computation without thinking about the underlying
cryptographic details. For example, \figureref{ex-sml}
shows an \tool source
program for $w^Tx >b$. The program is quite similar to what a programmer might
write in C++ or Java. The simplicity of the
language comes with the usual benefits: it is easily accessible to the
developers, there are fewer avenues for making mistakes, developers
don't bear the burden of getting cryptographic details right, 
code optimizations can be left to the compiler,
and it
is easy to maintain and modify the programs. Needless to say,
frameworks that expose low-level circuit APIs to the programmer do not
enjoy these benefits.

\subsubsection{Cryptographic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and generates non-cryptographic code for the array accesses.
Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an efficient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic-cost aware compiler.

\subsubsection{Scalability (secure code partitioning)} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool. 
%\aseem{What about the differences from Yao pipelining? Worth
%adding here that it is a backend-agnostic technique?}

@@

\subsubsection{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for all well-typed source programs, the two semantics
successfully terminate
(e.g., there are no array index out-of-bounds errors) with identical
observable outputs. For
the security theorem, we formally reduce the security
of our scheme against semi-honest (or ``honest but curious")
adversaries to the semi honest security of the  \mpc back-end. The
theorem provides protection against side-channels arising from
conditionals and memory access patterns.
 We also prove a formal security theorem against semi-honest
 adversaries for our partitioning
scheme (\sectionref{ld} and~\sectionref{pipe}).

\subsubsection{Evaluation}We implemented \tool
using ABY~\cite{aby} as the
cryptographic back-end.
We compare \tool with Yao-based compilers in~\sectionref{oblivm}
and with specialized protocols in~\sectionref{eval}. 
 We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers from Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also matrix factorization from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of \bonsai~\cite{bonsai}, and it was programmed in the
high-level \tool source language by a non-cryptographer. Second, the
performance
of the protocols
generated by \tool are comparable to or better than (up to 19x) their state-of-the-art, hand-crafted implementations. Finally, we
demonstrate the usefulness of partitioning by implementing an application
that requires more than 300 million gates (\sectionref{impl} and~\sectionref{eval}).

\noindent\textbf{Summary.} To summarize the above five points, the novelty of \tool is in implementing cryptographic cost awareness inside a compiler, allowing the programmers to program in a high-level language absent of all the cryptographic details, while the compiler chooses the best circuit representation (boolean or arithmetic) for different parts of the program and also handles interconversions between them -- all this in a provably secure manner. Prior compilers such as Wysteria, ObliVM, and CBMC-GC use backends with single representations (either boolean or arithmetic), and so the  challenges associated with multiple representations and interconversions are absent. Moreover, as shown in Section~\sectionref{oblivm}, they perform poorly on ML tasks that involve a mix of arithmetic and boolean computations. The work of Kerschbaum {\em et al.}~\cite{autoS} integrates a backend with both boolean and arithmetic represenations. However it operates over circuits represented as a sequence of dyadic operations, while \tool provides a high-level programming language with loops and branches. \tool compilation is automatic and sub-quadratic in the size of generated ABY programs (e.g. \figureref{ex-aby}) after switching off memory safety checking. In sharp contrast, \cite{autoS} describes approaches that would be doubly exponential and exponential in the length of ABY programs. Finally, our partitioning technique, unlike prior work, which is specific to and works on Yao’s garbled circuits, works at the source level and is agnostic to the cryptographic backend.

These features (ease-of-programming, use of multiple crypto backends, and scalability through partitioning) enable us to write and evaluate a wide array of ML algorithms such as matrix factorization with efficient generic 2PC techniques. Without \tool, this would have been a near-impossible task and has never been done.

\subsection{Related Work}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} observe, due
 to the high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries that lack formal semantics and static guarantees.
Finally, we focus on the language
features necessary to implement machine learning applications.
In particular, we do not discuss declassification of
intermediate values or indexing into arrays at secret indices.
 Handling them requires additional complexity. For example,
Wysteria~\cite{wysteria} handles the former using dependent types
and ObliVM~\cite{oblivm} uses Oblivious RAM for the latter.
These situations seldomly arise in the machine learning applications that we consider:
intermediate values don't need to be declassified and arrays are traversed in an oblivious manner. We provide a detailed survey of related
work in \sectionref{related}.

### 2018-07-29 ndss/pipe.tex
ccs comments.

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits.
Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and partitioning is independent of the specific
\mpc protocol. 
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in  \appendixref{codepartitioning}.

@@

>>>>

In this section, we describe our ``secure code partitioning'' technique that
allows \tool to execute programs that require large circuits. The reason to implement partitioning is as follows: when compiling from a high level functionality to a circuit being evaluated securely, the circuits so generated can quite often be larger than the total memory available. The secure protocol for evaluating this circuit cannot then be generated without swapping it in and out of main memory, thereby causing large slowdowns (see Section \ref{sec:pipeeval}). In order to avoid this problem, we ``split'' the high level functionality into smaller programs that compile into smaller circuits whose secure evaluation can completely fit into main memory. These smaller circuits are then evaluated sequentially to evaluate the entire program. Naturally, care must be taken to ensure that the partial evaluation of these circuits do not reveal any more information than the final output of the functionality. More details follow.

Our techniques take inspiration from the idea of pipelining Yao's garbled circuits described in FastGC \cite{yao-pipe}.
However, unlike FastGC, we do not operate at a circuit level and partitioning is independent of the specific
\mpc protocol. 
Let $\prog$ be a program in our source language that
generates a circuit $\crct$. For some programs, the circuit $\crct$
can be larger than
the memory size\footnote{In fact, there is
  an upper limit of $2^{32}-1$ gates for the circuit size in ABY but
  for most machines the memory limit is hit first.} and fail to
execute. Partitioning enables us to 
execute such programs via a source to source transformation that is
oblivious to the underlying \mpc backend. Partitioning decomposes the
program $\prog$ into a sequence of smaller \tool programs
$\progn_1,\progn_2,\ldots,\progn_k$ (as defined below) such
that the circuit size
requirement for each of the $\progn_i$ itself is manageable. We compile
and execute each $\progn_i$ sequentially, feeding the outputs of
$\progn_i$ as state
information to $\progn_{i+1}$. We prove our partitioning scheme to be
correct ($\prog$ and sequential execution of $\progn_1,\progn_2,\ldots,\progn_k$ compute
the same functionality) and secure (sequential execution of
$\progn_1,\progn_2,\ldots,\progn_k$ does
not reveal any more information than $\prog$). 
%
%Prior works such as FastGC \cite{yao-pipe} and ObliVM \cite{oblivm} have developed similar techniques specific to garbled circuits that work at the level of circuits.
%
%considered the idea of pipelining of circuits for secure computation based on Yao's garbled circuits that allows them to scale to large circuits. Our technique of secure code partitioning works with high level programs and does source code transformation. This gives a generic way to execute programs with large underlying circuits (even a mix of arithmetic and Boolean) and is not tied to the specific details of the cryptographic protocol used.
%}
More formal details follow, while an example illustrating the technique of secure code partitioning is provided in the full version. %\appendixref{codepartitioning}.

@@

We stress that partitioning is fully automated and is compatible with any 2PC protocol. Furthermore, the \tool compiler, with suitable changes to operator costs, can target other backends including 3PC or MPC, or protocols secure against malicious adversaries.
